Optimal (Multiway) Spatial Joins

### 2024-05-27 msj.tex
yufei

\noindent {\underline{\em Example 4.3.} Let us examine, in turn, the two 2-tuples $\bm{t}_1 = (\alpha', \beta_1')$ and $\bm{t}_2 = (\alpha', \beta_2')$ in $\J(R_1', R_2')$. For $\bm{t}_1$, $B_{\bm{t}_1}$ is the rectangle \ttt{ABCD}, and $\gleft(\bm{t}_1) = \gbot(\bm{t}_1) = \alpha'$. Accordingly, $\dcross_H(\bm{t}_1) = \set{h_2}$ and $\dcross_V(\bm{t}_1) = \set{v_3}$. For $\bm{t}_2$, $B_{\bm{t}_2}$ is the rectangle \ttt{AEFG}, and $\gleft(\bm{t}_1) = \gbot(\bm{t}_1) = \alpha'$. Accordingly, $\dcross_H(\bm{t}_2) = \set{h_2, h_4, h_5}$ and $\dcross_V(\bm{t}_1) = \set{v_3, v_4, v_5}$.
\qed

\vspace{1mm}
\vgap

@@

\extraspacing {\underline{\em Example 4.4.} In our running example, the $\J^*$ computed includes 10 tuples in total: $(\alpha, \beta_1, h_2, v_3)$, and $\{\alpha\} \times \{\beta_2\} \times \set{h_2, h_4, h_5} \times \set{v_3, v_4, v_5}$. All these 10 tuples belong to $\J(R_1, R_2, H, V)$ and include the 4 tuples in $\J_1$ (see Example 4.1).
\qed

\extraspacing {\bf Sets $\bm{R^*_1, R^*_2, ..., R^*_{k-2}}$.} Fix any $i \in [k-2]$. For each rectangle $r' \in R_i'$, define
\myeqn{
    \maxtop(r') &=& \max_{\bm{t} \in \J(R'_1, ..., R'_{k-2}): \gbot(\bm{t}) = r'} \ytop(B_\bm{t}). 
}
We set $\maxtop(r')$ to $-\infty$, if no $\bm{t} \in \J(R'_1, ..., R'_{k-2})$ has $r'$ as the $\gbot(\bm{t})$. When $\maxtop(r') \ne -\infty$, assuming $r' = [x_1, x_2] \times [y_1, y_2]$, we introduce a rectangle
\myeqn{
    r^* &=& [x_1, x_2] \times [y_1, \maxtop(r')]. \nn
}
and call it the {\em top-sliced rectangle} of $r'$.

\extraspacing {\underline{\em Example 4.4.}

>>>>

\noindent {\underline{\em Example 4.3.} Let us examine, in turn, the two 2-tuples $\bm{t}_1 = (\alpha', \beta_1')$ and $\bm{t}_2 = (\alpha', \beta_2')$ in $\J(R_1', R_2')$. For $\bm{t}_1$, $B_{\bm{t}_1}$ is the rectangle \ttt{ABCD} in Figure~\ref{fig:hv:type1:ex}c, and $\gleft(\bm{t}_1) = \gbot(\bm{t}_1) = \alpha'$. Accordingly, $\dcross_H(\bm{t}_1) = \set{h_2}$ and $\dcross_V(\bm{t}_1) = \set{v_3}$. For $\bm{t}_2$, $B_{\bm{t}_2}$ is the rectangle \ttt{AEFG}, and $\gleft(\bm{t}_1) = \gbot(\bm{t}_1) = \alpha'$. Accordingly, $\dcross_H(\bm{t}_2) = \set{h_2, h_4, h_5}$ and $\dcross_V(\bm{t}_1) = \set{v_3, v_4, v_5}$.
\qed

@@

\extraspacing {\underline{\em Example 4.4.} In our running example, the $\J^*$ computed includes 10 tuples: $(\alpha, \beta_1, h_2, v_3)$, and $\{\alpha\} \times \{\beta_2\} \times \set{h_2, h_4, h_5} \times \set{v_3, v_4, v_5}$. All these 10 tuples belong to $\J(R_1, R_2, H, V)$ and include the 4 tuples in $\J_1$ (see Example 4.1).
\qed

\extraspacing {\bf Sets $\bm{R^*_1, R^*_2, ..., R^*_{k-2}}$.} Fix any $i \in [k-2]$. Define for each $r' \in R_i'$:
\myeqn{
    \maxtop(r') &=& \max_{\bm{t} \in \J(R'_1, ..., R'_{k-2}): \gbot(\bm{t}) = r'} \ytop(B_\bm{t}). 
}
We set $\maxtop(r')$ to $-\infty$, if no $\bm{t} \in \J(R'_1, ..., R'_{k-2})$ has $r'$ as the $\gbot(\bm{t})$. When $\maxtop(r') \ne -\infty$, assuming $r' = [x_1, x_2] \times [y_1, y_2]$, we introduce a rectangle
\myeqn{
    r^* &=& [x_1, x_2] \times [y_1, \maxtop(r')]. \nn
}
and call it the {\em top-sliced rectangle} of $r'$.

%\vgap

\extraspacing {\underline{\em Example 4.5.} The two tuples $\bm{t}_1 = (\alpha', \beta_1')$ and $\bm{t}_2 = (\alpha', \beta_2')$ in $\J(R_1',$ $R_2')$ satisfy $\gbot(\bm{t}_1) = \gbot(\bm{t}_2) = \alpha'$. Therefore, $\maxtop(\alpha') = \max\{\ytop(B_{\bm{t}_1}), \ytop(B_{\bm{t}_2})\} = \max\{6, 9.5\} = 9.5$. The top-sliced rectangle of $r'$ is the rectangle $\alpha^*$ in Figure~\ref{fig:hv:type1:ex}d. Rectangles $\beta'_1$ and $\beta'_2$ do not have top-sliced rectangles.
\qed
